---
title: "graphic_description "
categorie: Data Sciences I
description: |visualisation of the weight in relation to the buayant weight of sea urchins on the farm and in the fishery.
author:
  - name: Franquit Derrick NGAMI
    url:
      http://franquit_ngami/blog: {}
  - name: Benedicte BOUCHET
    url: {}
  - name: Engels Guyliann
    url: https://guyliann.netlify.com/fr
date: 12-30-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
SciViews::R
```

```{r, echo=FALSE}
urchin <- read("urchin_bio", package = "data.io")
```
# Description

we have chosen the urchi_bio dataset which describes various measurements on Paracentrotus lividus sea urchins from fishing (Brittany, France), or from a sea urchin farm in Normandy, this dataset contains 19 variables.

# Graphique

```{r graphe }
chart(urchin, formula = weight ~ buoyant_weight %col=% origin %shape=% sex ) +
  geom_point(na.rm= TRUE)
```

This graph is a scatter plot showing weight versus buayant weight using colour to differentiate the origin of individuals and different shapes to differentiate the gender of individuals. The weight are proportional to their floating weight. Farmed sea urchins have a greater weight than fishery urchins. 
